\chapter{Introduction}
\label{ch:intro}

\section{Purpose}
The purpose of this document is to define the objectives and scope of the \textbf{[Project Name]}. This ensures that all stakeholders have a clear understanding of the project and agree on what will be delivered.


\section{Product Scope}
This section outlines the boundaries of the product, including the functionalities and features to be delivered. It also specifies any constraints and limitations, ensuring that expectations are aligned with project deliverables.

\section{Definitions, Acronyms, and Abbreviations}
\begin{itemize}
    \item \textbf{API}: Application Programming Interface
    \item \textbf{GUI}: Graphical User Interface
    \item \textbf{SDK}: Software Development Kit
\end{itemize}
Definitions and abbreviations relevant to this document are provided to ensure clarity and avoid any ambiguity.

\section{References}
This section lists references to other relevant documents or materials that were used in the creation of this document:
\begin{itemize}
    \item ISO/IEC 12207:2008 - Systems and software engineering — Software life cycle processes.
    \item Feasibility Study Report, Version 1.0.
\end{itemize}

\section{Overview}
This document is organized as follows:
\begin{itemize}
    \item Section~\ref{ch:intro} introduces the project, providing details about its purpose, scope, and relevant definitions.
    \item Section~2 outlines the technical specifications and requirements.
    \item Section~3 describes the design and implementation approach.
\end{itemize}

