\chapter{Overall Description}
\label{ch:overall_desc}

\section{Product Perspective}
This section provides a high-level view of the product, its background, and its positioning in the market.

\subsection{Market Status}
The current market landscape is reviewed to highlight existing solutions and gaps. This analysis provides the context for the product's development and its unique value proposition.

\subsection{Overall Structure}
The overall structure of the product is described, including its components and their interactions. This section provides a conceptual understanding of how the product operates.

\section{Product Functions}
The core functionalities of the product are outlined. Each function is briefly described to provide an understanding of the features that the product offers to its users.

\section{User Classes and Characteristics}
This section identifies the different types of users and their specific characteristics.

\subsection{User}
The end-user category includes individuals who interact with the product to achieve their objectives. Their roles, goals, and skill levels are described here.

\subsection{System Manager}
System managers are responsible for the maintenance and administration of the product. Their roles include configuration, monitoring, and troubleshooting.

\section{Operating Environment}
The operating environment outlines the conditions under which the product will function.

\subsection{Hardware}
The hardware requirements, including specifications for servers, devices, and peripherals, are listed here.

\subsection{Software}
The software environment, including operating systems, third-party applications, and dependencies required to run the product, is described.

\section{Implementation Constraints}
Any constraints that may impact the implementation of the product are identified. These can include technical limitations, regulatory requirements, or organizational policies.

\section{User Documentation}
This section outlines the documentation that will be provided to users, including manuals, tutorials, and online help resources.

\section{Assumptions and Dependencies}
The assumptions made during the product development and any dependencies on external systems, services, or technologies are detailed here.
