\chapter{Supporting Information}
\label{ch:supporting_information}

\section{Software Requirements}
This section lists the software requirements necessary for the system to function correctly. Table~\ref{tab:software_requirements} provides the details.

\begin{table}[h]
    \centering
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Software} & \textbf{Requirement} & \textbf{Specification} \\ \hline
        Operating System & Linux/Windows & Ubuntu 20.04 or later, Windows 10 \\ \hline
        Database & MySQL & Version 8.0 or higher \\ \hline
        Web Server & Nginx/Apache & Nginx 1.18+ or Apache 2.4+ \\ \hline
        Programming Language & Python & Version 3.8 or higher \\ \hline
        Framework & Django & Version 4.0 or higher \\ \hline
        Frontend Framework & React & Version 18.0 or higher \\ \hline
    \end{tabular}
    \caption{Software Requirements}
    \label{tab:software_requirements}
\end{table}

\section{Additional Resources}
This section provides information about additional resources that may be required for the project.

\subsection{Documentation}
The system includes comprehensive documentation:
\begin{itemize}
    \item User Manual: Instructions for end users.
    \item Developer Guide: Technical details for developers.
    \item API Documentation: Specifications for API usage.
\end{itemize}

\subsection{External Libraries and Tools}
The following libraries and tools are recommended:
\begin{itemize}
    \item \textbf{NumPy}: For numerical operations.
    \item \textbf{Pandas}: For data manipulation.
    \item \textbf{Matplotlib}: For visualizations.
    \item \textbf{Docker}: For containerization.
\end{itemize}

\section{System Compatibility}
The system is designed to be compatible with various hardware and software configurations. Compatibility details include:
\begin{itemize}
    \item \textbf{Browsers}: Chrome, Firefox, Edge.
    \item \textbf{Devices}: Desktop, tablet, mobile.
\end{itemize}

\section{Reference Materials}
For further information, the following materials are referenced:
\begin{itemize}
    \item Project Feasibility Study
    \item Industry Standards Documentation
    \item Third-Party Library Manuals
\end{itemize}
